Ricci-Ollivier curvature of two random walks on rooted phylogenetic subtree-prune-regraft graph

### 2015-02-24 curvature.tex
Typo.
Tiny comment.

We first consider properties of the uniform random walk on the rSPR graph.
Assume that the random walk begins at a tree $T$.
The uniform random walk selects a tree uniformly at random from $N(T)$.
We denote the curvature of the uniform random walk between two trees $T$ and $S$ with $\curvature{T,S}$.
Recall that $\curvature{T, S} := 1 - \frac{W_1(m_T, m_S)}{d(x, y)}$.
For the uniform random walk, $m_T$ is simply the set of neighbors of $T$ each assigned a mass of $\frac{1}{\degree{T}}$.

>>>>

We first consider properties of the uniform random walk on the rSPR graph.
Assume that the random walk begins at a tree $T$.
The uniform random walk selects a tree uniformly at random from $N(T)$.
We denote the curvature of the uniform random walk between two trees $T$ and $S$ with $\curvature{T,S}$.
Recall that $\curvature{T, S} := 1 - \frac{W_1(m_T, m_S)}{d(T, S)}$.
For the uniform random walk, $m_T$ is  simply the set
\todo{AlexG: Technically, $m_T$ is a measure on the set of vertices of the rSPR.}
of neighbors of $T$ each assigned a mass of $\frac{1}{\degree{T}}$.
